An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-27 VLDB2026/main.tex
Update main.tex

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/hybrid ANNS.pdf}
		\caption{Hybrid query example}

@@

	\setlength{\textfloatsep}{0cm}
	\setlength{\floatsep}{0cm}
	\begin{table*}[t]
		\centering
		%\setlength{\belowcaptionskip}{-0.3cm}
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.2cm}
		\caption{Comparison of AF-ANN search algorithms}
		\small
		\label{tab:compair_1}
		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			NHQ & Graph & C & Y & N& N& N & N & N \\
			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\

@@

		\centering
		%	 \setlength{\abovecaptionskip}{0cm}
		%	\setlength{\belowcaptionskip}{0.1cm}
		\footnotesize{
			\begin{minipage}{\linewidth}
				\vspace{0.1cm}
				\textsuperscript{A} Post-filtering, 
				\textsuperscript{B} Pre-filtering, 
				\textsuperscript{C} Simultaneous filtering, 
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport. 
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
				\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
				\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
		\end{minipage}}
		\vspace{-0.3cm}
	\end{table*}

@@

	\setlength{\textfloatsep}{0.1cm}
	\setlength{\floatsep}{0cm}
	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		\setlength{\textfloatsep}{0.1cm}
		\caption{Comparison of RF-ANN search algorithms}
		\small	% 只会影响当前组的内容
		\label{tab:range_algo}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			DSG & Graph & Y & N \\
			iRange & Graph & N & Y \\
			SeRF & Graph & Y & Y \\
			UNIFY & Graph & Y & Y \\
			WinFilter & Graph & N & Y  \\
			\hline
		\end{tabular}

		\footnotesize{
			\begin{minipage}{\linewidth}
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
			\end{minipage} 
		}

@@

	\setlength{\textfloatsep}{0.1cm}
	\setlength{\floatsep}{0cm}
	\begin{table}[t]
		\centering

		\setlength{\abovecaptionskip}{0.05cm}
		\setlength{\textfloatsep}{0.cm}
		\caption{Datasets}

		\label{tab:datasets_combined}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{cccccc}
				\toprule
				Dataset & Dimension & Base Data & Queries & LID & Type \\
				\midrule
				Msong & 420 & 992,272 & 200 & 23& Audio \\[2pt]
				Audio & 192 & 53,387 & 200 & 14& Audio \\[2pt]
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\[2pt]
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\[2pt]
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\[2pt]
				Enron & 1369 & 94,987 & 200 & 23& Text \\[2pt]
				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\[2pt]
				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\[2pt] 
				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\[2pt]
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\[2pt]

@@

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Index construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index size}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.3cm}
			\includegraphics[width=\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

@@

	\begin{figure*}
		\centering
		        \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

	\begin{figure*}
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

	\begin{figure}[th]
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		% 上面的图例，居中并可通过 hspace 调整左右位置
		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
		\includegraphics[width=0.98\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径

		% 下面的子图，居中显示
		\includegraphics[width=0.8\columnwidth]{figures/exp/exp_2_1.pdf}
		\caption{Effect of Multi-Attribute Index Construction on Single Query Performance. ($S$ denotes single-attribute index construction and single-attribute query; $M$ denotes multi-attribute index construction and single-attribute query)}
		\label{fig:exp_2_1}

>>>>

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
		\caption{Hybrid query example}

@@

	\setlength{\textfloatsep}{0cm}
	\setlength{\floatsep}{0cm}
	\renewcommand{\arraystretch}{0.9}
	\begin{table*}[t]
		\centering
		%\setlength{\belowcaptionskip}{-0.3cm}
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Comparison of AF-ANN search algorithms}
		\small
		\label{tab:compair_1}
		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			NHQ & Graph & C & Y & N& N& N & N & N \\
			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\

@@

		\centering
		%	 \setlength{\abovecaptionskip}{0cm}
		%	\setlength{\belowcaptionskip}{0.1cm}
		\footnotesize{
			\begin{minipage}{\linewidth}
				\vspace{0.1cm}
				\textsuperscript{A} Post-filtering, 
				\textsuperscript{B} Pre-filtering, 
				\textsuperscript{C} Simultaneous filtering, 
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport. 
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
				\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
				\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
		\end{minipage}}
		\vspace{-0.5cm}
	\end{table*}

@@

	\setlength{\textfloatsep}{0.1cm}
	\setlength{\floatsep}{0cm}
		\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		\setlength{\textfloatsep}{0.1cm}
		\caption{Comparison of RF-ANN search algorithms}
		\small	% 只会影响当前组的内容
		\label{tab:range_algo}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			DSG & Graph & Y & N \\
			iRange & Graph & N & Y \\
			SeRF & Graph & Y & Y \\
			UNIFY & Graph & Y & Y \\
			WinFilter & Graph & N & Y  \\
			\hline
		\end{tabular}

		\footnotesize{
			\begin{minipage}{\linewidth}
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
			\end{minipage} 
			\vspace{-0.1cm}
		}

@@

	\setlength{\textfloatsep}{0.1cm}
	\setlength{\floatsep}{0cm}
	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering

		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Datasets}

		\label{tab:datasets_combined}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{cccccc}
				\toprule
				Dataset & Dimension & Base Data & Queries & LID & Type \\
				\midrule
				Msong & 420 & 992,272 & 200 & 23& Audio \\
				Audio & 192 & 53,387 & 200 & 14& Audio \\
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\
				Enron & 1369 & 94,987 & 200 & 23& Text \\
				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\

@@

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Index construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index size}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0cm}
			\setlength{\belowcaptionskip}{-0.3cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

@@

	\begin{figure*}
		\centering
		        \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

	\begin{figure*}
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.98\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		% 上面的图例，居中并可通过 hspace 调整左右位置
		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
		\includegraphics[width=0.95\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径

		% 下面的子图，居中显示
		\includegraphics[width=0.7\columnwidth]{figures/exp/exp_2_1.pdf}
		\caption{Effect of Multi-Attribute Index Construction on Single Query Performance. ($S$ denotes single-attribute index construction and single-attribute query; $M$ denotes multi-attribute index construction and single-attribute query)}
		\label{fig:exp_2_1}
